Topology and experimental distinguishability

### 2017-07-29 Articles/TopologyAndExperimentalDistinguishability/article.tex
Going through the proofs with Christine

\begin{proof}
	To show that the conjunction is well defined it suffices to show that we can construct a suitable experimental test.  Let $\mathsf{e}_\wedge=\mathsf{e}_\wedge(\{\mathsf{e}_i\}_{i=1}^{n})$ be the experimental procedure defined as follows:
	\begin{enumerate}
	\item for each $i=1,\ldots,n$ run the test $\mathsf{e}_i$
	\item if all tests $\mathsf{e}_i$ terminate successfully, terminate the test $\mathsf{e}_\wedge$ successfully.
	\end{enumerate}
	This experimental procedure terminates successfully if and only if all $\mathsf{e}_i$ terminate successfully. It will do so in finite time as each of the finitely many $\mathsf{e}_i$ succeeds in finite time. Therefore $\mathsf{e}_\wedge(\{\mathsf{e}_i\}_{i=1}^{n})$ is an experimental test that is successful if and only if all statements $\{\mathsf{s}_i\}_{i=1}^{n}$ are true. So, $\bigwedge\limits_{i=1}^{n} \mathsf{o}_i = \llparenthesis\bigwedge\limits_{i=1}^{n} \mathsf{s}_i, \mathsf{e}_{\wedge}(\mathsf{e}_i)\rrparenthesis$ is an experimental observation.
\end{proof}

@@

\begin{proof}
	As before, it suffices to show that we can construct a suitable experimental test. Let $\mathsf{e}_\vee=\mathsf{e}_\vee(\{\mathsf{e}_i\}_{i=1}^{\infty})$ be the experimental procedure defined as follows:
	\begin{enumerate}
	\item initialize $n$ to 1
	\item for each $i=1,\ldots,n$:
	\begin{enumerate}
		\item run the test $\mathsf{e}_i$ for $n$ seconds
		\item if $\mathsf{e}_i$ terminated successfully, terminate $\mathsf{e}_\vee$ successfully
	\end{enumerate}
	\item increment $n$ and go to step 2
	\end{enumerate}
	Suppose there exists an $i \in \mathbb{Z}^+$ such that $\mathsf{e}_i$ will terminate successfully. Then the above procedure will eventually run that test for time sufficient for it to terminate successfully. It will do so in finite time as it will have run finitely many tests finitely many times each for a finite amount of time. Therefore $\mathsf{e}_\vee(\{\mathsf{e}_i\}_{i=1}^{\infty})$ is an experimental test that is successful if and only if at least one statement in $\{\mathsf{s}_i\}_{i=1}^{n}$ is successful. So $\bigvee\limits_{i=1}^{\infty} \mathsf{o}_i =\llparenthesis\bigvee\limits_{i=1}^{\infty} \mathsf{s}_i, \mathsf{e}_{\wedge}(\{\mathsf{e}_i\}_{i=1}^{\infty})\rrparenthesis$ is an experimental observation.
\end{proof}

@@

\begin{proof}
	We show that the finite intersection of verifiable sets is a verifiable set. Let $U_1, U_2, ... , U_n \subseteq X$ be n verifiable sets. For each $U_i$ there exists an experimental observation $\mathsf{o}_i = \llparenthesis x\in U_i, \mathsf{e}_\in(U_i) \rrparenthesis$. Consider the finite conjunction $\mathsf{o} = \bigwedge\limits_{i=1}^{n} \mathsf{o}_i = \llparenthesis \bigwedge\limits_{i=1}^{n} x\in U_i , \mathsf{e}_{\wedge}(\mathsf{e}_\in(U_i)) \rrparenthesis=\llparenthesis x\in \bigcap\limits_{i=1}^{n} U_i, \mathsf{e}_\in(\bigcap\limits_{i=1}^{n} U_i)\rrparenthesis$ which is an experimental observation. Thus $\bigcap\limits_{i=1}^{n} U_i$ is a verifiable set.

@@

\begin{thm}
A set of experimentally distinguishable possibilities $X$ has a natural Hausdorff, second-countable topology $(X,\mathsf{T})$ with the open sets given by the verifiable sets of the associated experimental identification domain $(\mathcal{D}_X, X, x)$.
\end{thm}
\begin{proof}
First, from the definition one can see that for all $x\in X$, there exists a verifiable set $U$ with $x\in U$. Therefore the union of a (countable) basis is the verifiable set $X$. Further, there exist at least two incompatible experimental observation, corresponding to two disjoint sets, so the empty set is a verifiable set. Now, \ref{setbehavior} shows that the collection $\mathsf{T}$ is closed under finite intersection and countable union. Because $\mathsf{T}$ is determined by an experimental domain of observations, there is a countable basis of operations which translates to a countable basis of open (verifiable) sets, so it is second-countable. To show it is closed under arbitrary union, notice that an arbitrary union may be rewritten as a union of basis elements, which is then a countable union, and so it remains in $\mathsf{T}$. That the topology is Hausdorff is immediate from the last part of the definition. 
\end{proof}

@@

\begin{prop}
	The experimental relationship $f$ defined above is a continuous function.
\end{prop}
\begin{proof}
Let $o_y = \llparenthesis y\in U_Y,\mathsf{e}_{\in}(U_Y)\rrparenthesis \in \mathcal{D}_Y$.  Since $f$ can be used within an experimental test, consider the following experimental procedure:
\begin{enumerate}
	\item map $x$ to $y=f(x)$
	\item run the test $\mathsf{e}_{\in}(U_Y)$
\end{enumerate}
It will be successful if and only if $y \in U_Y$. Since $y=f(x)$, it is successful if and only if $x \in f^{-1}(U_Y)$: the procedure is the test $\mathsf{e}_{\in}(f^{-1}(U_Y))$. This means that $o_x = \llparenthesis x \in f^{-1}(U_Y),\mathsf{e}_{\in}(f^{-1}(U_Y))\rrparenthesis$ is an experimental observation and it must be in $\mathcal{D}_X$ since $\mathcal{D}_X$ contains all possible experimental observations of that form. It follows that $f^{-1}(U_Y)$ is a verifiable set and must be part of the topology $\mathsf{T}_X$.
\end{proof}

\begin{defn}[Experimental relationship between observations]
	Let $(\mathcal{D}_X, X, x)$ and $(\mathcal{D}_Y, Y, y)$ be two experimental identification domains. An \textbf{experimental relationship} is a map $g : \mathcal{D}_Y \rightarrow \mathcal{D}_X$ such that if $\mathsf{o} \in \mathcal{D}_Y$ is verified then $g(\mathsf{o}) \in \mathcal{D}_X$ must also be verified. To be consistent, such relationship must have these properties:
	\begin{enumerate}
	\item it is compatible with conjunction and disjunction: for any $\mathsf{o}_1, \mathsf{o}_2 \in \mathcal{D}_y$, we have $g(\mathsf{o}_1 \wedge \mathsf{o}_2)=g(\mathsf{o}_1)\wedge g(\mathsf{o}_2)$ and $g(\mathsf{o}_1 \vee \mathsf{o}_2)=g(\mathsf{o}_1)\vee g(\mathsf{o}_2)$
	\item contradiction leads to contradiction: $g(\bot) = \bot$
	\item no knowledge leads to no knowledge: if $Y$ is the verifiable set associated with $\mathsf{o} \in \mathcal{D}_Y$ then $X$ is the verifiable set associated with  $g(\mathsf{o})$
	\end{enumerate}
\end{defn}

@@

\begin{proof}
	First we reformulate $g$ in terms of the open set. We can redefine $g: \mathsf{T}_Y \rightarrow \mathsf{T}_X$ to be the map between the verifiable sets corresponding to the experimental observations. This map has the following properties:
	\begin{enumerate}
		\item It is compatible with union and intersection, i.e. for any subsets $V_1, V_2 \subseteq Y$, we have $g(V_1 \cup V_2)=g(V_1)\cup g(V_2)$ and $g(V_1 \cap V_2)=g(V_1)\cap g(V_2)$
		\item $g(\emptyset) = \emptyset$
		\item $g(Y) = X$
	\end{enumerate}

	Then we construct the unique extension $\bar{g}:\sigma(Y)\to\sigma(X)$ to the Borel $\sigma$-algebras of $X$ and $Y$, respectively $\sigma(X)$ and $\sigma(Y)$, such that $\bar{g}|_{\mathsf{T}_Y}=g$ and $\bar{g}$ is compatible with union, intersection and complements. Let $\bar{g}(V) = g(V)$ for all open sets $V \in \mathsf{T}_Y$. Let $A \in \sigma(Y)$ (not necessarily open) and $A^C$ be its complement. We must have $\bar{g}(A^C) = \bar{g}(A)^C = X\setminus \bar{g}(A)$ for $\bar{g}$ to be compatible with complements. Recall that all Borel sets in $\sigma(Y)$ and $\sigma(X)$ may be written as some combination of unions, intersections, and complements of open sets. Thus, the construction uniquely determine what $\bar{g}$ should output on any Borel set. We need only check that the output is still a Borel set. But by definition of $\bar{g}$, the outputs will be given as unions, intersections, and complements of outputs of $g$, which are open sets, and so the image of $\bar{g}$ is contained in $\sigma(X)$.  $\bar{g}$ is well defined. The function $\bar{g}$ in a sense represents extracting the maximum amount of information possible out of $g$.

	Next we define $\hat{g}:Y\to\sigma(X)$ such that $\hat{g}(y) = \bar{g}(\{y\})$. Since $Y$ is Hausdorff, every singleton $\{y\}$ is closed and is therefore a Borel set. Therefore $\bar{g}(\{y\})$ is well defined and so is $\hat{g}(y)$.

@@

	We are now ready to define $f: X\to Y$ such that $f(x) = y$ if and only if $x\in \hat{g}(y)$. Since $g(Y)=X$, there exists $y\in Y$ such that $x\in\hat{g}(y)$. By the preceding claim, this $y$ is unique. $f: X\to Y$ is well defined. Note that no arbitrary choice where made so far that lead to the construction of $f$, which is therefore determined uniquely by $g$.

	Now we show that $g = f^{-1} |_{\mathsf{T}(Y)}$. Let $V\in\mathsf{T}(Y)$. We want to show $f^{-1}(V) = g(V)$. Let $x\in f^{-1}(V)$. Then for some $y \in V$ we have $f(x)=y$. $x\in \hat{g}(y)$ by construction of $f$. $\hat{g}(y) \subset g(V)$ since $\{y\}\subset V$, so $x\in g(V)$. $f^{-1}(V) \subseteq g(V)$. Conversely, let $x\in g(V)=\bar{g}(V)$. Then for some $y\in V$, we have $x\in\bar{g}(\{y\})\subset\bar{g}(V)$. But then by definition we have $f(x)=y$, so $x\in f^{-1}(V)$. $f^{-1}(V) \supseteq g(V)$. $f^{-1}(V) = g(V)$ for all $V\in\mathsf{T}(Y)$ and therefore $f^{-1}|_{\mathsf{T}(Y)}=g$.

	Lastly we claim $f$ is continuous. It is so since $g = f^{-1} |_{\mathsf{T}(Y)}$ takes open sets to open sets. 
\end{proof}

@@

\begin{proof}
	As we saw in the previous result, both definitions lead to experimental relationships being fully characterized by a continuous function.
\end{proof}

@@

\begin{prop}
	Let $X$ and $Y$ be two Hausdorff and second-countable topological spaces. Let $C(X,Y)$ denote the set of all continuous functions from $X$ to $Y$. Let $\mathcal{B}_X$ and $\mathcal{B}_Y$ be two countable bases for $X$ and $Y$ respectively. The basis-to-basis topology $\mathsf{T}(C(X,Y), \mathcal{B}_X, \mathcal{B}_Y)$ on $C(X,Y)$ with respect to the basis $\mathcal{B}_X$ and $\mathcal{B}_Y$ is Hausdorff and second-countable. 
\end{prop}
\begin{proof}
	First we show that $\mathsf{T}(C(X,Y), \mathcal{B}_X, \mathcal{B}_Y)$ is second-countable. We note that the sub-basis $\{V(U_X, U_Y) \, |\,   U_X \in \mathcal{B}_X , U_Y \in \mathcal{B}_Y \}$ is countable since $\mathcal{B}_X$ and $\mathcal{B}_Y$ are countable and so will be the bases which it generates. Which means $\mathsf{T}(C(X,Y), \mathcal{B}_X, \mathcal{B}_Y)$ is second-countable.

	Next we show that $\mathsf{T}(C(X,Y), \mathcal{B}_X, \mathcal{B}_Y)$ is Hausdorff. Let $f,g:X\to Y$ be two distinct continuous functions. Then for some $x\in X$, we have $f(x)\neq g(x)$. Pick $V_1, V_2$ disjoint open subsets of $Y$ with $f(x)\in V_1$ and $g(x)\in V_2$. We may assume (possibly by shrinking $V_1$ or $V_2$) that both are basis elements for the topology of $Y$. Let $U=f^{-1}(V_1)\cap g^{-1}(V_2)$. Then $U$ is an open neighborhood of $x$. We may assume again that $U$ is a basis element for the topology on $X$ by shrinking it if necessary. Now, let $T_1$ to be the (sub-)basis element for basis-to-basis topology corresponding to $U$ and $V_1$. By construction, $f\in T_1$. Similarly, let $T_2$ to be the basis element for the basis-to-basis topology corresponding to $U$ and $V_2$ and containing $g$. Since $V_1$ and $V_2$ are disjoint, so are $T_1$ and $T_2$. $\mathsf{T}(\mathcal{C})$ is Hausdorff.
\end{proof}

@@

What emerges from this work is that \emph{the primary application of topology in science is experimental distinguishability}. Its role is to track of what can be distinguished through experimentation. The importance of continuous functions in science and physics is explained since experimental relationships have to be consistent with what can be experimentally distinguished. This provides a strong justification as to why deterministic systems are always characterized by continuous transformations. It is not that they happen to be continuous: they must be.

@@

\section*{Acknowledgments}
Funding for this work was provided in part by the MCubed program of the University of Michigan. The third author is supported by the National Science Foundation Graduate Research Fellowship Program under Grant No. DGE\#1256260. Any opinions, findings, and conclusions or recommendations expressed in this material are those of the author(s) and do not necessarily reflect the views of the National Science Foundation.

>>>>

\begin{proof}
	To show that the conjunction is well defined it suffices to show that we can construct a suitable experimental test.  Let $\mathsf{e}_\wedge=\mathsf{e}_\wedge(\{\mathsf{e}_i\}_{i=1}^{n})$ be the experimental procedure defined as follows:
	\begin{enumerate}
	\item for each $i=1,\ldots,n$ run the test $\mathsf{e}_i$
	\item if all tests $\mathsf{e}_i$ terminate successfully then terminate successfully
	\end{enumerate}
	This experimental procedure terminates successfully if and only if all $\mathsf{e}_i$ terminate successfully. It will do so in finite time as each of the finitely many $\mathsf{e}_i$ succeeds in finite time. Therefore $\mathsf{e}_\wedge(\{\mathsf{e}_i\}_{i=1}^{n})$ is an experimental test that is successful if and only if all statements $\{\mathsf{s}_i\}_{i=1}^{n}$ are true. So, $\bigwedge\limits_{i=1}^{n} \mathsf{o}_i = \llparenthesis\bigwedge\limits_{i=1}^{n} \mathsf{s}_i, \mathsf{e}_{\wedge}(\mathsf{e}_i)\rrparenthesis$ is an experimental observation.
\end{proof}

@@

\begin{proof}
	As before, it suffices to show that we can construct a suitable experimental test. Let $\mathsf{e}_\vee=\mathsf{e}_\vee(\{\mathsf{e}_i\}_{i=1}^{\infty})$ be the experimental procedure defined as follows:
	\begin{enumerate}
	\item initialize $n$ to 1
	\item for each $i=1,\ldots,n$:
	\begin{enumerate}
		\item run the test $\mathsf{e}_i$ for $n$ seconds
		\item if $\mathsf{e}_i$ terminated successfully then terminate successfully
	\end{enumerate}
	\item increment $n$ and go to step 2
	\end{enumerate}
	Suppose there exists an $i \in \mathbb{Z}^+$ such that $\mathsf{e}_i$ will terminate successfully. Then the above procedure will eventually run that test for sufficient time for it to terminate successfully. It will do so in finite time as it will have run finitely many tests finitely many times each for a finite amount of time. Therefore $\mathsf{e}_\vee(\{\mathsf{e}_i\}_{i=1}^{\infty})$ is an experimental test that is successful if and only if at least one statement in $\{\mathsf{s}_i\}_{i=1}^{\infty}$ is successful. So $\bigvee\limits_{i=1}^{\infty} \mathsf{o}_i =\llparenthesis\bigvee\limits_{i=1}^{\infty} \mathsf{s}_i, \mathsf{e}_{\vee}(\{\mathsf{e}_i\}_{i=1}^{\infty})\rrparenthesis$ is an experimental observation.
\end{proof}

@@

\begin{proof}
	We show that the finite intersection of verifiable sets is a verifiable set. Let $U_1, U_2, ... , U_n \subseteq X$ be $n$ verifiable sets. For each $U_i$ there exists an experimental observation $\mathsf{o}_i = \llparenthesis x\in U_i, \mathsf{e}_\in(U_i) \rrparenthesis$. Consider the finite conjunction $\mathsf{o} = \bigwedge\limits_{i=1}^{n} \mathsf{o}_i = \llparenthesis \bigwedge\limits_{i=1}^{n} x\in U_i , \mathsf{e}_{\wedge}(\mathsf{e}_\in(U_i)) \rrparenthesis=\llparenthesis x\in \bigcap\limits_{i=1}^{n} U_i, \mathsf{e}_\in(\bigcap\limits_{i=1}^{n} U_i)\rrparenthesis$ which is an experimental observation. Thus $\bigcap\limits_{i=1}^{n} U_i$ is a verifiable set.

@@

\begin{thm}
A set of experimentally distinguishable possibilities $X$ has a natural Hausdorff, second-countable topology $(X,\mathsf{T})$ with the open sets given by the verifiable sets of the associated experimental identification domain $(\mathcal{D}_X, X, x)$.
\end{thm}
\begin{proof}
First, from the definition one can see that for all $x\in X$, there exists a verifiable set $U$ with $x\in U$. Therefore the union of a (countable) basis is the verifiable set $X$. Further, there exist at least two incompatible experimental observations, corresponding to two disjoint sets, so the empty set is a verifiable set. Now, \ref{setbehavior} shows that the collection $\mathsf{T}$ is closed under finite intersection and countable union. Because $\mathsf{T}$ is determined by an experimental domain, there is a countable basis of observations which translates to a countable basis of open (verifiable) sets, so it is second-countable. To show it is closed under arbitrary union, notice that an arbitrary union may be rewritten as a union of basis elements, which is then a countable union, and so it remains in $\mathsf{T}$. That the topology is Hausdorff is immediate from the last part of the definition. 
\end{proof}

@@

\begin{prop}
	The experimental relationship $f$ defined above is a continuous function.
\end{prop}
\begin{proof}
Let $o_y = \llparenthesis y\in U_Y,\mathsf{e}_{\in}(U_Y)\rrparenthesis \in \mathcal{D}_Y$.  Since $f$ can be used within an experimental test, consider the following experimental procedure:
\begin{enumerate}
	\item map $x$ to $y=f(x)$
	\item run the test $\mathsf{e}_{\in}(U_Y)$
\end{enumerate}
It will be successful if and only if $y \in U_Y$. Since $y=f(x)$, it is successful if and only if $x \in f^{-1}(U_Y)$: the procedure is the test $\mathsf{e}_{\in}(f^{-1}(U_Y))$ on $x$. This means that $o_x = \llparenthesis x \in f^{-1}(U_Y),\mathsf{e}_{\in}(f^{-1}(U_Y))\rrparenthesis$ is an experimental observation and it must be in $\mathcal{D}_X$ since $\mathcal{D}_X$ contains all possible experimental observations of that form. It follows that $f^{-1}(U_Y)$ is a verifiable set and must be part of the topology $\mathsf{T}_X$.
\end{proof}

\begin{defn}[Experimental relationship between observations]
	Let $(\mathcal{D}_X, X, x)$ and $(\mathcal{D}_Y, Y, y)$ be two experimental identification domains. An \textbf{experimental relationship} is a map $g : \mathcal{D}_Y \rightarrow \mathcal{D}_X$ such that if $\mathsf{o} \in \mathcal{D}_Y$ is verified then $g(\mathsf{o}) \in \mathcal{D}_X$ must also be verified. To be consistent, such a relationship must have these properties:
	\begin{enumerate}
	\item it is compatible with conjunction and disjunction: for any $\mathsf{o}_1, \mathsf{o}_2 \in \mathcal{D}_y$, we have $g(\mathsf{o}_1 \wedge \mathsf{o}_2)=g(\mathsf{o}_1)\wedge g(\mathsf{o}_2)$ and $g(\mathsf{o}_1 \vee \mathsf{o}_2)=g(\mathsf{o}_1)\vee g(\mathsf{o}_2)$
	\item contradiction leads to contradiction: $g(\bot) = \bot$
	\item no knowledge leads to no knowledge: if $Y$ is the verifiable set associated with $\mathsf{o} \in \mathcal{D}_Y$ then $X$ is the verifiable set associated with  $g(\mathsf{o})$
	\end{enumerate}
\end{defn}

@@

\begin{proof}
	First we reformulate $g$ in terms of the open set. We can redefine $g: \mathsf{T}_Y \rightarrow \mathsf{T}_X$ to be the map between the verifiable sets corresponding to the experimental observations. This map has the following properties:
	\begin{enumerate}
		\item it is compatible with union and intersection, i.e. for any subsets $V_1, V_2 \subseteq Y$, we have $g(V_1 \cap V_2)=g(V_1)\cap g(V_2)$ and $g(V_1 \cup V_2)=g(V_1)\cup g(V_2)$
		\item $g(\emptyset) = \emptyset$
		\item $g(Y) = X$
	\end{enumerate}

	Then we construct the unique extension $\bar{g}:\sigma_Y\to\sigma_X$ to the Borel $\sigma$-algebras of $X$ and $Y$, respectively $\sigma_X$ and $\sigma_Y$, such that $\bar{g}|_{\mathsf{T}_Y}=g$ and $\bar{g}$ is compatible with union, intersection and complements. Let $\bar{g}(V) = g(V)$ for all open sets $V \in \mathsf{T}_Y$. Let $A \in \sigma_Y$ (not necessarily open) and $A^C$ be its complement. We must have $\bar{g}(A^C) = \bar{g}(A)^C = X\setminus \bar{g}(A)$ for $\bar{g}$ to be compatible with complements. Recall that all Borel sets in $\sigma_Y$ and $\sigma_X$ may be written as some combination of unions, intersections, and complements of open sets. Thus, the construction uniquely determines what $\bar{g}$ should output on any Borel set. We need only check that the output is still a Borel set. But by definition of $\bar{g}$, the outputs will be given as unions, intersections, and complements of outputs of $g$, which are open sets, and so the image of $\bar{g}$ is contained in $\sigma_X$.  $\bar{g}$ is well defined.

	Next we define $\hat{g}:Y\to\sigma_X$ such that $\hat{g}(y) = \bar{g}(\{y\})$. Since $Y$ is Hausdorff, every singleton $\{y\}$ is closed and is therefore a Borel set. Therefore $\bar{g}(\{y\})$ is well defined and so is $\hat{g}(y)$.

@@

	We are now ready to define $f: X\to Y$ such that $f(x) = y$ if and only if $x\in \hat{g}(y)$. Since $g(Y)=X$, there exists $y\in Y$ such that $x\in\hat{g}(y)$. By the preceding claim, this $y$ is unique. $f: X\to Y$ is well defined. Note that no arbitrary choices were made so far that led to the construction of $f$, which is therefore determined uniquely by $g$.

	Now we show that $g = f^{-1} |_{\mathsf{T}_Y}$. Let $V\in\mathsf{T}_Y$. We want to show $f^{-1}(V) = g(V)$. Let $x\in f^{-1}(V)$. Then for some $y \in V$ we have $f(x)=y$. $x\in \hat{g}(y)$ by construction of $f$. $\hat{g}(y) \subset g(V)$ since $\{y\}\subset V$, so $x\in g(V)$. $f^{-1}(V) \subseteq g(V)$. Conversely, let $x\in g(V)=\bar{g}(V)$. Then for some $y\in V$, we have $x\in\bar{g}(\{y\})\subset\bar{g}(V)$. But then by definition we have $f(x)=y$, so $x\in f^{-1}(V)$. $f^{-1}(V) \supseteq g(V)$. $f^{-1}(V) = g(V)$ for all $V\in\mathsf{T}_Y$ and therefore $f^{-1}|_{\mathsf{T}_Y}=g$.

	Lastly we claim $f$ is continuous. It is so since $g = f^{-1} |_{\mathsf{T}_Y}$ takes open sets to open sets. 
\end{proof}

@@

\begin{proof}
	As we saw in the previous results, both definitions lead to experimental relationships being fully characterized by a continuous function.
\end{proof}

@@

\begin{prop}
	Let $X$ and $Y$ be two Hausdorff and second-countable topological spaces. Let $C(X,Y)$ denote the set of all continuous functions from $X$ to $Y$. Let $\mathcal{B}_X$ and $\mathcal{B}_Y$ be two countable bases for $X$ and $Y$ respectively. The basis-to-basis topology $\mathsf{T}(C(X,Y), \mathcal{B}_X, \mathcal{B}_Y)$ on $C(X,Y)$ with respect to the bases $\mathcal{B}_X$ and $\mathcal{B}_Y$ is Hausdorff and second-countable. 
\end{prop}
\begin{proof}
	First we show that $\mathsf{T}(C(X,Y), \mathcal{B}_X, \mathcal{B}_Y)$ is second-countable. We note that the sub-basis $\{V(U_X, U_Y) \, |\,   U_X \in \mathcal{B}_X , U_Y \in \mathcal{B}_Y \}$ is countable since $\mathcal{B}_X$ and $\mathcal{B}_Y$ are countable and so will be the bases which it generates. This means $\mathsf{T}(C(X,Y), \mathcal{B}_X, \mathcal{B}_Y)$ is second-countable.

	Next we show that $\mathsf{T}(C(X,Y), \mathcal{B}_X, \mathcal{B}_Y)$ is Hausdorff. Let $f,g:X\to Y$ be two distinct continuous functions. Then for some $x\in X$, we have $f(x)\neq g(x)$. Pick $V_1, V_2$ disjoint open subsets of $Y$ with $f(x)\in V_1$ and $g(x)\in V_2$. We may assume (possibly by shrinking $V_1$ or $V_2$) that both are basis elements for the topology of $Y$. Let $U=f^{-1}(V_1)\cap g^{-1}(V_2)$. Then $U$ is an open neighborhood of $x$. We may assume again that $U$ is a basis element for the topology on $X$ by shrinking it if necessary. Now, let $T_1$ be the (sub-)basis element for the basis-to-basis topology corresponding to $U$ and $V_1$. By construction, $f\in T_1$. Similarly, let $T_2$ be the basis element for the basis-to-basis topology corresponding to $U$ and $V_2$ and containing $g$. Since $V_1$ and $V_2$ are disjoint, so are $T_1$ and $T_2$. $\mathsf{T}(C(X,Y), \mathcal{B}_X, \mathcal{B}_Y)$ is Hausdorff.
\end{proof}

@@

What emerges from this work is that the primary application of topology in science is experimental distinguishability: its role is to keep track of what can be distinguished through experimentation. The importance of continuous functions in science stems from requiring that experimental relationships be consistent with experimental distinguishability. Therefore it is not that the deterministic evolution of a physical system happens to be continuous: it must be.

@@

\section*{Acknowledgments}
Funding for this work was provided in part by the MCubed program of the University of Michigan.
